Title

### 2014-01-09 paper/paper.tex
Added Titles and Names

% Title, Author, and Address Information
\title{Followers are not enough: Beyond structure in the detection of communities \\
Followers are not enough: Exploring the communities that exist beyond structure \\
Followers are Not Enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
Followers are not enough: Beyond structural communities in online social networks
 \\
 Followers are not enough: exploring communities beyond structure
\\
 }
  \author{David Darmon \\
 Address line\\
 Address line\\
 \And Elisa Omodei \\
 LaTTiCe (CNRS, ENS, Paris 3)\\
ISC-PIF\\
elisa.omodei@ens.fr \\
 \And 
 Joshua Garland\\
 University of Colorado at Boulder\\
Dept. of Computer Science
joshua.garland@colorado.edu}

>>>>

% Title, Author, and Address Information
\title{
%Followers are not enough: Beyond structure in the detection of communities \\
Followers are not enough: Exploring the communities that exist beyond structure \\
%Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
%Followers are not enough: Beyond structural communities in online social networks
% \\
 %Followers are not enough: exploring communities beyond structure
 }
  \author{David Darmon  \\
 University of Maryland\\
Dept. of Mathematics \\
ddarmon@math.umd.edu \\
 \And Elisa Omodei \\
 LaTTiCe (CNRS, ENS, Paris 3)\\
ISC-PIF\\
elisa.omodei@ens.fr \\
 \And 
 Joshua Garland\\
 University of Colorado at Boulder\\
Dept. of Computer Science \\
joshua.garland@colorado.edu}
